Predictive analytics in quality assurance for assembly processes: lessons learned from a case study at an industry 4.0 demonstration cell

### 2020-11-26 02_Paper/paper.tex
worked on comments

The quality control of production processes and products is one fundamental part of the general quality management. It contains the measures and activities needed to fulfill specific quality requirements \cite{illes2017new}.
According to Illés, there are three established tools and methods of quality control \cite{illes2017new}:
The Statistical Process Control (SPC), Auditing and Total Quality Control (TQC).   
The SPC is normally used to monitor the production process using recorded data values for the quality characteristics, as well as to indicate any significant changes
in the quality characteristics in the production process \cite{selvamuthu2018introduction}. This method can take place right before and/or after a manufacturing process and be implemented as an "off-line" or "in-line" SPC.
\AP{@Lennart, last sentence is still quite confising to me}

@@

\AP{100\% method is not introduced}

Product and process auditing is the independent examination of product and process quality to provide information and it is considered the most fundamental quality control technique. This method is executed by
an independent auditor, who based on sampling or checking records limits the finding on reporting incorrect processes procedures or products documentation. In a further step, the findings would be later corrected by other than the auditor \cite{fox1993quality}.

@@

While the SPC mostly optimizes the capability of the process, for example the acceptance plan prevents the nonconforming product to be pass and then delivered to the next process or the customer \cite{kurniati2015quality}.
In the case of a hundred percent control, this is associated with higher costs and a higher requirement of time, compared to a quality control based on a machine learning model.
Statistical methods are faster as \AP{as "or" "than"} hundred percent controls, but have the same problem like the SPC: Because they are based on assumptions, this methods are prone to errors,
if the variance of the product quality is to high.
The concept of TQC is to extend the scope of quality control to the whole company and product life cycle,
by involving all departments of the organization \cite{illes2017new}.
The quality characteristics of a product can be classified as variables or attributes.
Variables are measurable characteristics, which are shown as numbers. On the contrary,
attributes are not measureable and can only take the value go or no-go \cite{mitra2016fundamentals}. 
The advantage of variable measurements is that in the event of a defective intermediate or end product, 
precise measured values are available, which enable precise adjustment of the process parameters. 
This allows the desired quality to be restored. With that in mind, a predictive quality control is a promising solution.

>>>>

The quality control of production processes and products is one fundamental part of the general quality management. It contains the measures and activities needed to fulfill specific quality requirements \cite{illes2017new}.
According to Illés, there are three established tools and methods of quality control \cite{illes2017new}:
The Statistical Process Control (SPC), Auditing and Total Quality Control (TQC).   
The SPC is normally used to monitor the production process using recorded data values for the quality characteristics, as well as to indicate any significant changes
in the quality characteristics in the production process \cite{selvamuthu2018introduction}. This method can also take place before the actual manufacturing process in form of an "off-line SPC". During the designing phase of a process or product,
off-line SPC procedueres are aiming to select and choose controllable product and process parameters to increase the quality of the outcoming product \cite{mitra2016fundamentals}.
\AP{@Lennart, last sentence is still quite confising to me}

@@

\AP{100\% method is not introduced}
The contrary method to any statistical method, is the hundred percent control, where every product is controlled and sorted by being an ok or non-ok part.
Product and process auditing is the independent examination of product and process quality to provide information and it is considered the most fundamental quality control technique. This method is executed by
an independent auditor, who based on sampling or checking records limits the finding on reporting incorrect processes procedures or products documentation. In a further step, the findings would be later corrected by other than the auditor \cite{fox1993quality}.

@@

While the SPC mostly optimizes the capability of the process, for example the acceptance plan prevents the nonconforming product to be pass and then delivered to the next process or the customer \cite{kurniati2015quality}.
In the case of a hundred percent control, this is associated with higher costs and a higher requirement of time, compared to a quality control based on a machine learning model.
Statistical methods are faster than hundred percent controls, but have the same problem like the SPC: Because they are based on assumptions, this methods are prone to errors,
if the variance of the product quality is to high.
The concept of TQC is to extend the scope of quality control to the whole company and product life cycle,
by involving all departments of the organization \cite{illes2017new}.
The quality characteristics of a product can be classified as variables or attributes.
Variables are measurable characteristics, which are shown as numbers. On the contrary,
attributes are not measureable and can only take the value go or no-go \cite{mitra2016fundamentals}. 
The advantage of variable measurements is that in the event of a defective intermediate or end product, 
precise measured values are available, which enable precise adjustment of the process parameters. 
This allows the desired quality to be restored. With that in mind, a predictive quality control is a promising solution.
